Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-10 paper/paper.tex
added distinct to the definition of the complement
Anonymouse

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
\newcommand{\loopcomp}[1]{\overset{\multimap}{#1}}
% to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {?? [}{#1}{]}}}

@@

\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
Research Council [grant number EP/K503058/1]} \and Craig Reilly\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M506539/1]} \\
University of Glasgow, Glasgow, Scotland \\
ruth.hoffmann@glasgow.ac.uk \and \{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}

\pdfinfo{
    /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
    /Author (Ruth Hoffmann and Ciaran McCreesh and Craig Reilly)
}

@@

\begin{abstract}
    \todo{anonymise abstract}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is known as the maximum
    common subgraph problem, which is much more computationally challenging in practice than
    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
    vertices from the pattern can be found in the target graph. This allows for the development of
    slightly weakened forms of certain invariants from subgraph isomorphism which are based upon degree and
    number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
    their effectiveness. We are then able to solve this problem on the standard SIP problem
    instances used to benchmark subgraph isomorphism algorithms, despite these instances being
    too large for current maximum common subgraph algorithms to handle.
\end{abstract}
\todo{try code on MCS instances}
\section{Introduction}
\todo{talk about subgraph isomorphism applications, particularly vision}
\todo{talk about reformulating}
The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs
\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.

@@

The \emph{complement} of a (simple) graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are
non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.  The \emph{loop complement} of a graph $P$ is the graph $\loopcomp{P}$.  The constructcion of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an induced subgraph isomorphism problem we make use of the loop complement; we care about mapping vertices with loops to vertices with loops, and edges without loops to vertices without loops.  (Although when we filter by paths we make use of the complement rather than the loop complement.)  The following proposition follows directly from the definitions.

@@

\begin{figure}
    \includegraphics*{gen-graph-ids.pdf}
    \caption{We get domain filtering. Woohoo.}\label{figure:ids}
\end{figure}

@@

\begin{figure*}
    \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
    \includegraphics*{gen-graph-constraints-induced.pdf}
    \caption{We get new constraints. More woohoo.}\label{figure:constraints}
\end{figure*}

@@

\begin{figure}
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{Look how amazing our stuff is.}\label{figure:runtimes}
\end{figure}

@@

\begin{figure}
    \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{There are satisfiable instances for small values of $k$. Yay.}\label{figure:which-k}
\end{figure}

@@

\begin{figure}
    \includegraphics*{gen-graph-versus-cp.pdf}
    \caption{A righteous spanking.}\label{figure:versus-cp}
\end{figure}

@@

\section*{Acknowledgements}

We're not going to thank anyone, no, no.  Thanks to Frances for making us less smelly throughout the writing of the paper (by thieving toiletries from a fancy hotel).

>>>>

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
\newcommand{\loopcomp}[1]{\oset[.1ex]{\multimap}{#1}}
% to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {?? [}{#1}{]}}}

\makeatletter
\newcommand{\oset}[3][0ex]{%
  \mathrel{\mathop{#3}\limits^{
    \vbox to#1{\kern-2\ex@
    \hbox{$\scriptstyle#2$}\vss}}}}
\makeatother

@@

\author{Anonymous \and Anonymous\thanks{This work was supported by an anonymous funding agency [grant number 12345]} \and Anonymous\thanks{This work was supported by an anonymous funding agency [grant number 67890]} \\
Top Secret Research Lab, Atlantis \\
anonymous@anonymous}

\pdfinfo{
    /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
    /Author (Anonymous and Anonymous and Anonymous)
}

@@

\begin{abstract}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is known as the maximum
    common subgraph problem, which is much more computationally challenging in practice than
    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
    vertices from the pattern can be found in the target graph. This allows for the development of
    slightly weakened forms of certain invariants from subgraph isomorphism which are based upon degree and
    number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
    their effectiveness. We are then able to solve this problem on the standard SIP problem
    instances used to benchmark subgraph isomorphism algorithms, despite these instances being
    too large for current maximum common subgraph algorithms to handle.
\end{abstract}
\todo{try code on MCS instances}
\section{Introduction}
\todo{talk about subgraph isomorphism applications, particularly vision}
\todo{talk about reformulating}
The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs
\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.

@@

The \emph{complement} of a (simple) graph $P$ is the graph $\bar{P}~$.  Adjacent distinct vertices in $P$ are non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.  The \emph{loop complement} of a graph $P$ is the graph $\loopcomp{P}$.  The constructcion of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an induced subgraph isomorphism problem we make use of the loop complement; we care about mapping vertices with loops to vertices with loops, and edges without loops to vertices without loops.  (Although when we filter by paths we make use of the complement rather than the loop complement.)  The following proposition follows directly from the definitions.

@@

\begin{figure}
    % \includegraphics*{gen-graph-ids.pdf}
    \caption{We get domain filtering. Woohoo.}\label{figure:ids}
\end{figure}

@@

\begin{figure*}
    % \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
    % \includegraphics*{gen-graph-constraints-induced.pdf}
    \caption{We get new constraints. More woohoo.}\label{figure:constraints}
\end{figure*}

@@

\begin{figure}
    % \includegraphics*{gen-graph-runtimes.pdf}
    \caption{Look how amazing our stuff is.}\label{figure:runtimes}
\end{figure}

@@

\begin{figure}
    % \includegraphics*{gen-graph-which-k-by-family.pdf}
    \caption{There are satisfiable instances for small values of $k$. Yay.}\label{figure:which-k}
\end{figure}

@@

\begin{figure}
    % \includegraphics*{gen-graph-versus-cp.pdf}
    \caption{A righteous spanking.}\label{figure:versus-cp}
\end{figure}

@@

% \section*{Acknowledgements}
% 
% Thanks to Christine, Samba, Patrick.
